The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2017-02-03 brains-protocol.tex
formatting: add figure placement indications for manuscript format

\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/all-feature_correlations.png}
    \caption{Spearman correlations in the initial set of features}
    \label{fig:feature-corrs-initial}
\end{figure}

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.6412\linewidth]{images/computed-figures/paper-feature_correlations-v2.png}
    \caption{Spearman correlations in the filtered set of features}
    \label{fig:feature-corrs-filtered}
\end{figure}

@@

\begin{figure}[h]
    \centering
	\def\svgwidth{\linewidth}
	\small
	\input{images/substitution-unmodelled.pdf_tex}
	\caption{{\bf Possible paths from occurrence to occurrence.}
	\newtext{$q$, $q'$ and $q''$ are three quotation variants belonging to the same cluster.
	$q$ and $q''$ differ by two words, but $q'$ differs from both $q$ and $q''$ by one word.
	The second occurrence of $q$ can safely be considered a faithful copy of the first, but the occurrences of $q'$ and $q''$ are uncertain:
	while the first occurrence of $q'$ is most likely a substitution from $q$, it could also stem from $q''$;
	conversely, the second occurrence of $q''$ could also be a substitution from $q'$ instead of being a faithful copy of its first occurrence.}
	}
	\label{fig:substitution-unmodelled}
\end{figure}

@@

	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=all-Past=last_bin-Durl=all.pdf_tex}
	    \caption{Source can be anything, destination can be anything\\\hfill} % \\\hfill to add a line, aligning with the other panels which have two-line captions
	    \label{fig:substitution-modelled-all-all}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=all-Past=last_bin-Durl=exclude_past.pdf_tex}
	    \caption{Source can be anything, destination must not appear in preceding bin}
	    \label{fig:substitution-modelled-all-exclude_past}
	\end{subfigure}
	\caption{\newtext{
	{\bf Substitution models.}
	Substitutions inferred by four models in the situation introduced by Fig.~\ref{fig:substitution-unmodelled}.
	Each of these models uses bins spanning 1 day aligned to midnight (see the main text for a complete description of parameters).
	In the top left panel~(a), $q$ holds the majority in the first bin and is considered the unique basis for $q'$ in bin~2.
	$q'$ and $q''$ have equal maximum frequency in bin~2 however, so both are sources of substitutions towards bin~3.
	In the top right panel~(b), quotes that appear in the preceding bin cannot be the target of a substitution; this removes two substitutions compared to panel~(a).
	In the bottom left panel~(c), the majority constraint is lifted compared to panel~(a), making $q''$ in bin~1 a candidate source for $q'$ in bin~2.
	In the bottom right panel~(d), the majority constraint is also lifted compared to panel~(a) (adding the same $q'' \rightarrow q'$ substitution as in panel~(c)), and the excluded-past constraint is added as in panel~(b) (removing the two same substitutions from bin~2 to bin~3 as in panel~(b)).
	If the bins were extended to the beginning of the quotation family, the excluded-past constraint would also remove the $q' \rightarrow q$ substitution from bin~2 to bin~3.
	In all four panels, a background rectangle or square indicates the quotation is the source of a substitution.
	A thick border on that rectangle or square indicates the quotation was selected because it has maximum frequency.}
	}
    \label{fig:substitution-modelled}
\end{figure*}

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/all-susceptibilities-pos.png}
    \caption{\newtext{\textbf{POS-related results:}
    categories are simplified from the TreeTagger tag set: \emph{C} means \emph{Closed class-like} (see main text for details), \emph{J} means adjective, \emph{N}~noun, \emph{R}~adverb, and \emph{V} means verb.
    The top panel shows the actual $s_{POS}$ and $s_{POS}^0$ counts. The bottom panel shows the substitution susceptibility $\sigma_{POS}$, which is the ratio between the two previous counts.
    Confidence intervals are computed with the \citet{goodman_simultaneous_1965} method for multinomial proportions.}
    }
    \label{fig:pos-susceptibilities}
\end{figure}

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/paper-susceptibilities-quantilebins_global.png}
    \caption{\textbf{Substitution susceptibility for feature values:}
    susceptibility to substitution versus feature value of a candidate word for substitution \newtext{(binned by quartiles)}, with 95\% asymptotic confidence intervals \newtext{(Goodman-based multinomial)}.
    }
    \label{fig:feature-susceptibilities-global}
\end{figure*}

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/paper-variations-quantilebins_global.png}
    \caption{\textbf{Feature variation upon substitution:}
    $\nu_\phi$, average feature value of the appearing word as a function of the feature value of the disappearing word in a substitution \newtext{(binned by quartiles)}, with 95\% asymptotic confidence intervals based on Student's \emph{t}-distribution.
    The overall position of the curve with respect to the dashed line representing $\mathcal{H}_0$ (constant $\nu_{\phi}^0$) indicates the direction of the cognitive bias \newtext{compared to a purely random variation}.
    \newtext{The position with respect to the dash-dotted line representing $\mathcal{H}_{00}$ ($\nu_{\phi}^{00}$) indicates the bias compared to a semantically plausible random variation obtained by choosing a random synonym of the disappearing word.}
    The intersection with $y = x$ marks the attractor value.
    The fact that all curves have slopes smaller than 1 \newtext{in absolute value} means that the substitution operation is contractile on average:
    \newtext{it brings} each feature \newtext{closer to} its own specific asymptotic range.
    }
    \label{fig:feature-variations-global}
\end{figure*}

@@

@@

@@

>>>>

\indicatemanfigure{fig:feature-corrs-initial}
\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/all-feature_correlations.png}
    \caption{Spearman correlations in the initial set of features}
    \label{fig:feature-corrs-initial}
\end{figure}

@@

\indicatemanfigure{fig:feature-corrs-filtered}
\begin{figure}[!th]
    \centering
    \includegraphics[width=0.6412\linewidth]{images/computed-figures/paper-feature_correlations-v2.png}
    \caption{Spearman correlations in the filtered set of features}
    \label{fig:feature-corrs-filtered}
\end{figure}

@@

\indicatemanfigure{fig:substitution-unmodelled}
\begin{figure}[h]
    \centering
	\def\svgwidth{\linewidth}
	\small
	\input{images/substitution-unmodelled.pdf_tex}
	\caption{{\bf Possible paths from occurrence to occurrence.}
	\newtext{$q$, $q'$ and $q''$ are three quotation variants belonging to the same cluster.
	$q$ and $q''$ differ by two words, but $q'$ differs from both $q$ and $q''$ by one word.
	The second occurrence of $q$ can safely be considered a faithful copy of the first, but the occurrences of $q'$ and $q''$ are uncertain:
	while the first occurrence of $q'$ is most likely a substitution from $q$, it could also stem from $q''$;
	conversely, the second occurrence of $q''$ could also be a substitution from $q'$ instead of being a faithful copy of its first occurrence.}
	}
	\label{fig:substitution-unmodelled}
\end{figure}

@@

	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=all-Past=last_bin-Durl=all.pdf_tex}
	    \caption{Source can be anything, destination can be anything\ifapamode{}{\\\hfill}{}} % apamode man/jou/doc. \\\hfill to add a line, aligning with the other panels which have two-line captions
	    \label{fig:substitution-modelled-all-all}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=all-Past=last_bin-Durl=exclude_past.pdf_tex}
	    \caption{Source can be anything, destination must not appear in preceding bin}
	    \label{fig:substitution-modelled-all-exclude_past}
	\end{subfigure}
	\caption{\newtext{
	{\bf Substitution models.}
	Substitutions inferred by four models in the situation introduced by Fig.~\ref{fig:substitution-unmodelled}.
	Each of these models uses bins spanning 1 day aligned to midnight (see the main text for a complete description of parameters).
	In the top left panel~(a), $q$ holds the majority in the first bin and is considered the unique basis for $q'$ in bin~2.
	$q'$ and $q''$ have equal maximum frequency in bin~2 however, so both are sources of substitutions towards bin~3.
	In the top right panel~(b), quotes that appear in the preceding bin cannot be the target of a substitution; this removes two substitutions compared to panel~(a).
	In the bottom left panel~(c), the majority constraint is lifted compared to panel~(a), making $q''$ in bin~1 a candidate source for $q'$ in bin~2.
	In the bottom right panel~(d), the majority constraint is also lifted compared to panel~(a) (adding the same $q'' \rightarrow q'$ substitution as in panel~(c)), and the excluded-past constraint is added as in panel~(b) (removing the two same substitutions from bin~2 to bin~3 as in panel~(b)).
	If the bins were extended to the beginning of the quotation family, the excluded-past constraint would also remove the $q' \rightarrow q$ substitution from bin~2 to bin~3.
	In all four panels, a background rectangle or square indicates the quotation is the source of a substitution.
	A thick border on that rectangle or square indicates the quotation was selected because it has maximum frequency.}
	}
    \label{fig:substitution-modelled}
\end{figure*}

@@

\indicatemanfigure{fig:substitution-modelled}

@@

\indicatemanfigure{fig:pos-susceptibilities}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/all-susceptibilities-pos.png}
    \caption{\newtext{\textbf{POS-related results:}
    categories are simplified from the TreeTagger tag set: \emph{C} means \emph{Closed class-like} (see main text for details), \emph{J} means adjective, \emph{N}~noun, \emph{R}~adverb, and \emph{V} means verb.
    The top panel shows the actual $s_{POS}$ and $s_{POS}^0$ counts. The bottom panel shows the substitution susceptibility $\sigma_{POS}$, which is the ratio between the two previous counts.
    Confidence intervals are computed with the \citet{goodman_simultaneous_1965} method for multinomial proportions.}
    }
    \label{fig:pos-susceptibilities}
\end{figure}

@@

\indicatemanfigure{fig:feature-susceptibilities-global}
\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/paper-susceptibilities-quantilebins_global.png}
    \caption{\textbf{Substitution susceptibility for feature values:}
    susceptibility to substitution versus feature value of a candidate word for substitution \newtext{(binned by quartiles)}, with 95\% asymptotic confidence intervals \newtext{(Goodman-based multinomial)}.
    }
    \label{fig:feature-susceptibilities-global}
\end{figure*}

@@

\indicatemanfigure{fig:feature-variations-global}
\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/paper-variations-quantilebins_global.png}
    \caption{\textbf{Feature variation upon substitution:}
    $\nu_\phi$, average feature value of the appearing word as a function of the feature value of the disappearing word in a substitution \newtext{(binned by quartiles)}, with 95\% asymptotic confidence intervals based on Student's \emph{t}-distribution.
    The overall position of the curve with respect to the dashed line representing $\mathcal{H}_0$ (constant $\nu_{\phi}^0$) indicates the direction of the cognitive bias \newtext{compared to a purely random variation}.
    \newtext{The position with respect to the dash-dotted line representing $\mathcal{H}_{00}$ ($\nu_{\phi}^{00}$) indicates the bias compared to a semantically plausible random variation obtained by choosing a random synonym of the disappearing word.}
    The intersection with $y = x$ marks the attractor value.
    The fact that all curves have slopes smaller than 1 \newtext{in absolute value} means that the substitution operation is contractile on average:
    \newtext{it brings} each feature \newtext{closer to} its own specific asymptotic range.
    }
    \label{fig:feature-variations-global}
\end{figure*}

@@

\indicatemanfigure{fig:feature-variations_regression-global}

@@

\indicatemanfigure{fig:feature-susceptibilities-in_sentence}

@@

\indicatemanfigure{fig:feature-variations-sentencerel}
